\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-03 3-advanced.Rmd
data fusion + matching

Data fusion is a process that consider combining multiple multiple data sources and it has been applied widely in the remote sensing community.

Meteorological and hydrological data have been matched in the applied studies in the literature to understand drought, ... [ref]. To be a valid pair of matching, the matched pair from different data sources need to

@@

>>>>

To be a valid pair of matching, the matched pair from different data sources need to

@@

This functionality can be seen as a matching [@stuart2010matching; @mcintosh2018using] exercise in the spatio-temporal domain to pair up nearby observatoins. It can also be considered as a form of data fusion [@castanedo2013review; @cocchi2019data], where data from multiple sources are combined together.

### 2022-02-03 main.tex
data fusion + matching

Data fusion is a process that consider combining multiple multiple data
sources and it has been applied widely in the remote sensing community.

Meteorological and hydrological data have been matched in the applied
studies in the literature to understand drought, \ldots{} {[}ref{]}. To
be a valid pair of matching, the matched pair from different data
sources need to

@@

>>>>

To be a valid pair of matching, the matched pair from different data
sources need to

@@

This functionality can be seen as a matching
\citep{stuart2010matching, mcintosh2018using} exercise in the
spatio-temporal domain to pair up nearby observatoins. It can also be
considered as a form of data fusion
\citep{castanedo2013review, cocchi2019data}, where data from multiple
sources are combined together.
